A Match Made in Landfills?

### 2023-04-07 3 Analysis Scripts/StatiscalAnalysis_ModelFitting.qmd
Updates to manuscript and statistical analysis

# save fit results table  
model1 %>%
  saveRDS(here("4 Results", "Models", "LMERmodel1.rds"))

@@

model2 <- broom::tidy(lmer_fit2_5)
print(model2)

@@

BLp <- plot_model(lmer_fit2_5,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Total Antibiotic Resistant Gene Burden'))

>>>>

# save fit results table  
model1 %>%
  saveRDS(here("4 Results", "Models", "GLMERmodel1.rds"))

@@

model2 <- broom::tidy(lmer_fit2_global)
print(model2)

@@

BLp <- plot_model(lmer_fit2_global,terms = 's.lui', type="pred", 
           show.data = TRUE, show.values = TRUE, show.p = TRUE,
           title = "", show.legend = TRUE, line.size=1,
           axis.title = c("Landfill Use Index",'Total Antibiotic Resistant Gene Burden'))

### 2023-04-07 5 Manuscript/manuscript/Manuscript.qmd
Edits to full statistical analysis
Updates to manuscript and statistical analysis

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

```{r}
library(tidyverse)
library(here)

@@

Presence absence ARG results obtained from the fecal samples between 2020 to 2021 were used for simple summary statistics. Samples were classified as "multiresistant" if they were resistant to three or more of the 8 antibiotic classes that we evaluated for in this study (Blanco-Peña et al., 2017). In addition, we applied the following formula to estimate the percentage of bacteria harboring ARGs: x = 10\[2+0.33(ct16S-ctARG)\], where x individual percent gene burden in the sample (i.e., the estimated number of copies of the gene present per reaction). Results were expressed in log10, ranging from −8 ( zero to a negligible amount of the bacteria in the sample carried an ARG) to 2 (all or 100% of the bacteria in the sample carried an ARG). The inverse Log10 was then applied to results so they could be totalled and used to evalute total gene burdens accross sampling periods.

@@

@tbl-summarytable shows a summary of the data.

Note the loading of the data providing a **relative** path using the `../../` notation. (Two dots means a folder up). You never want to specify an **absolute** path like `C:\ahandel\myproject\results\` because if you share this with someone, it won't work for them since they don't have that path. You can also use the `here` R package to create paths. See examples of that below.

```{r}
#| label: tbl-summarytable
#| tbl-cap: "Data summary table."
#| echo: FALSE
#resulttable=readRDS("../../results/summarytable.rds")
#knitr::kable(resulttable)
```

@@

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Height and weight stratified by gender."
#| echo: FALSE
knitr::include_graphics(here("3 Analysis Scripts","LUIvsBurden_LME.tiff"))
knitr::include_graphics(here("3 Analysis Scripts","LUIvsMDR_LME.tiff"))
```

@@

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Linear model fit table."
#| echo: FALSE
ModelAIC1 = readRDS(here("4 Results", "Tables", "ModelAIC1.rds"))
ModelAIC1
knitr::kable(ModelAIC1)

ModelAIC2 = readRDS(here("4 Results", "Tables", "ModelAIC2.rds"))
knitr::kable(ModelAIC2)
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# load a few R packages
library(here)
library(knitr)
```

@@

```{r, warning=FALSE}
library(tidyverse)
library(here)

@@

Presence absence ARG results obtained from the fecal samples between 2020 to 2021 were used for simple summary statistics. Samples were classified as "multiresistant" if they were resistant to three or more of the 8 antibiotic classes that we evaluated for in this study (Blanco-Peña et al., 2017). In addition, we applied the following formula to estimate the percentage of bacteria harboring ARGs: x = 10\[2+0.33(ct16S-ctARG)\], where x individual percent gene burden in the sample (i.e., the estimated number of copies of the gene present per reaction). Results were expressed in log10, ranging from −8 ( zero to a negligible amount of the bacteria in the sample carried an ARG) to 2 (all or 100% of the bacteria in the sample carried an ARG). The inverse Log10 was then applied to results so they could be totaled and used to evaluate total gene burdens across sampling periods.

@@

@@

```{r}
#| label: Figure1
#| fig-cap: "Total antimicrobial gene burden as predicted by the variables landfill use index, age, sampling period, and nest success."
#| echo: FALSE
knitr::include_graphics(here("3 Analysis Scripts","LUIvsBurden_LME.tiff"))

#| label: Figure2
#| fig-cap: "Multi-drug resistance as predicted by the variables landfill use index and age."
#| echo: FALSE
knitr::include_graphics(here("3 Analysis Scripts","LUIvsMDR_LME.tiff"))
```

@@

Binomial generalized linear mixed models (GLMMs) were used to predict multi-drug resistance (MDR) in White Storks, with nest identification classified as a random effects parameter. Of these, the highest performing model contained the predictors landfill use index (LUI) and age (@Table1). In this model, an increase in the age of the bird was associated with a higher likelihood of MDR being present (@Table2), while an increase in LUI was found to be associated with a decreased likelihood of MDR presence. A second competitive model, with a 97.20% performance score, contained only age as the predictor.

Linear mixed models (LMMs) were used to predict total antimicrobial gene burden in White Storks, with nest identification again classified as a random effects parameter. The global model, containing the variables landfill use index, age, sample period, and nest success, was the highest performing model (@Table3). In this model, each variable was positively correlated with antimicrobial gene burden (@Table4). The next highest performing model contained age as a single predictor, with a model performance score of 86.39%.

```{r}
#| label: Table1
#| tbl-cap: "Small sample adjusted Akaike's Information Criteria (AICc) model weights and performance scores for binomial generalized linear mixed models predicting multi-drug resistance in White Storks (Ciconia ciconia) in Madrid, Spain. "
#| echo: FALSE
ModelAIC1 = readRDS(here("4 Results", "Tables", "ModelAIC1.rds"))
knitr::kable(ModelAIC1)

#| label: Table2
#| tbl-cap: "Parameter estimates for fixed and random effects parameters and standard error of the highest performing model predicting multi-drug resistance in White Storks in Madrid, Spain."
#| echo: FALSE
GLMERmodel1 = readRDS(here("4 Results", "Tables", "GLMERmodel1.rds"))
knitr::kable(GLMERmodel1)

```{r}
#| label: Table3
#| tbl-cap: "Small sample adjusted Akaike's Information Criteria (AICc) model weights and performance scores for linear mixed models predicting total antimicrobial gene burden in White Storks (Ciconia ciconia) in Madrid, Spain. "
#| echo: FALSE
ModelAIC2 = readRDS(here("4 Results", "Tables", "ModelAIC2.rds"))
knitr::kable(ModelAIC2)

#| label: Table4
#| tbl-cap: "Parameter estimates for fixed and random effects parameters and standard error of the highest performing model predicting total antimicrobial gene burden in White Storks in Madrid, Spain."
#| echo: FALSE
GLMERmodel1 = readRDS(here("4 Results", "Tables", "LMERmodel2.rds"))
knitr::kable(GLMERmodel1)
